\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2015-04-18 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
merged the two tomography sections of the manual

\chapter{Doing tomography, i.e., updating the model based on the sensitivity kernels obtained}

@@

@@

\chapter{\label{cha:tomo}Tomographic inversion using sensitivity kernels}

Whatever misfit function you use for the tomographic inversion (several
examples in \citet{TrTaLi05} and \citet{TrKoLi08}), you will weight
the sensitivity kernels with measurements. Furthermore, you will use
as many measurements (stations, components, time windows) as possible
per event; hence, we call these composite kernels ``event kernels,''
which are volumetric fields representing the gradient of the misfit
function with respect to one of the variables (\eg $V_{{\rm s}}$).
The basic features of an adjoint-based tomographic inversion were
illustrated in \citet{TaLiTr07} and \citet{TrKoLi08} using a conjugate-gradient
algorithm; there are dozens of versions of gradient-based inversion
algorithms that could alternatively be used. The tomographic inversion
of \citet{TaLiMaTr09,TaLiMaTr2010} used SPECFEM3D Cartesian as well
as several additional components which are also stored on the CIG
svn server, described next.

The directory containing external utilities for tomographic inversion using
SPECFEM3D Cartesian (or other packages that evaluate misfit functions
and gradients) is in directory \texttt{utils/ADJOINT\_TOMOGRAPHY\_TOOLS/}:
\begin{verbatim}
flexwin/     -- FLEXWIN algorithm for automated picking of time windows
measure_adj/ -- reads FLEXWIN output file and makes measurements,
                with the option for computing adjoint sources
iterate_adj/ -- various tools for iterative inversion
                (requires pre-computed "event kernels")
\end{verbatim}
This directory also contains
a brief \verb+README+ file indicating the role of the three subdirectories,
\verb+flexwin+ \citep{Maggi2009}, \verb+measure_adj+, and \verb+iterate_adj+.
The components for making the model update are there; however, there
are no explicit rules for computing the model update, just as with
any optimization problem. There are options for computing a conjugate
gradient step, as well as a source subspace projection step. The workflow
could use substantial ``stitching together,'' and we welcome suggestions;
undoubtedly, the tomographic inversion procedure will improve with
time. \textbf{This is a work in progress.}

>>>>

\chapter{\label{cha:tomo}Doing tomography, i.e., updating the model based on the sensitivity kernels obtained}

@@

\section{Tomographic inversion / imaging using the sensitivity kernels obtained}

OLD VERSION OF THE SECTION, WILL SOON BE IMPROVED AND ENRICHED.\\

Whatever misfit function you use for the tomographic inversion (you can find several
examples in \citet{TrKoLi08} and \citet{TrTaLi05}), you will weight
the sensitivity kernels with measurements. Furthermore, you will use
as many measurements (stations, components, time windows) as possible
per event; hence, we call these composite kernels ``event kernels,''
which are volumetric fields representing the gradient of the misfit
function with respect to one of the variables (\eg $V_{{\rm s}}$).
The basic features of an adjoint-based tomographic inversion were
illustrated in \citet{TaLiTr07} and \citet{TrKoLi08} using a conjugate-gradient
algorithm; there are dozens of versions of gradient-based inversion
algorithms that could alternatively be used. The tomographic inversion
of \citet{TaLiMaTr09,TaLiMaTr2010} used SPECFEM3D Cartesian as well
as several additional components which are also stored on the CIG
svn server, described next.

The directory containing external utilities for tomographic inversion using
SPECFEM3D Cartesian (or other packages that evaluate misfit functions
and gradients) is in directory \texttt{utils/ADJOINT\_TOMOGRAPHY\_TOOLS/}:
\begin{verbatim}
flexwin/     -- FLEXWIN algorithm for automated picking of time windows
measure_adj/ -- reads FLEXWIN output file and makes measurements,
                with the option for computing adjoint sources
iterate_adj/ -- various tools for iterative inversion
                (requires pre-computed "event kernels")
\end{verbatim}
This directory also contains
a brief \verb+README+ file indicating the role of the three subdirectories,
\verb+flexwin+ \citep{Maggi2009}, \verb+measure_adj+, and \verb+iterate_adj+.
The components for making the model update are there; however, there
are no explicit rules for computing the model update, just as with
any optimization problem. There are options for computing a conjugate
gradient step, as well as a source subspace projection step.

@@
